Verified Nanopasses for Compiling Conditionals

### 2025-08-11 paper.tex
one more

\usepackage{url}
\usepackage{mathpartir}
\usepackage{listings}
\usepackage{stmaryrd}

@@

Towards developing a course on verified compilation, I am interested
in adapting verification techniques from CompCert to the compiler
presented in the \emph{Essentials of Compilation}
textbook~\citep{Siek:2023tr,Siek:2023ue}. That book takes an
incremental approach to teaching compilers, that is, it guides the
students through the creation of multiple compilers for a sequence of
languages, each of which adds a language feature to the previous
language. For the language with Boolean expressions and conditionals,
the Explicate Control pass of the compiler uses the one-function per
context approach of Danvy to translate into an x86-flavored register
transfer language.  \emph{Essentials of Compilation} also employs the
nanopass approach, breaking up the compiler into many small passes
that are easier for student to digest~\citep{Sarkar:2004fk}.  There
are many other pedogogical treatments of
compilation~\citep{Appel:2003fk,Sumii:2005aa,Aho:2006wb,Cooper:2011aa,Grune:2012aa};
what makes the \emph{Essentials of Compilation} unique is that it is
the first textbook to apply the incremental approach.  However,
\emph{Essentials of Compilation} does not include material about the
formal verification of compilers; hence my present interest.

>>>>

\usepackage{url}
\usepackage{mathpartir}
\usepackage{listings}
\usepackage{stmaryrd}
%\usepackage[none]{hyphenat}

@@

Towards developing a course on verified compilation, I am interested
in adapting these verification techniques to the compiler
presented in the \emph{Essentials of Compilation}
textbook~\citep{Siek:2023tr,Siek:2023ue}. That book takes an
incremental approach to teaching compilers, that is, it guides the
students through the creation of multiple compilers for a sequence of
languages, each of which adds a language feature to the previous
language. For the language with Boolean expressions and conditionals,
the Explicate Control pass of the compiler uses the one-function per
context approach of Danvy to translate into an x86-flavored register
transfer language.  \emph{Essentials of Compilation} also employs the
nanopass approach, breaking up the compiler into many small passes
that are easier for student to digest~\citep{Sarkar:2004fk}.  There
are many other pedogogical treatments of
compilation~\citep{Appel:2003fk,Sumii:2005aa,Aho:2006wb,Cooper:2011aa,Grune:2012aa};
what makes the \emph{Essentials of Compilation} unique is that it is
the first textbook to apply the incremental approach.  However,
\emph{Essentials of Compilation} does not include material about the
formal verification of compilers; hence my present interest.
